Correspondence Analysis of Two Mode Networks

### 2025-01-27 main-R1.tex
Updates from Overleaf

\subsection{Empirical Example} \label{subsec:ex}
Figure~\ref{fig:p-refs} shows the trajectory of the HH reflective centralities for persons in the Southern Women data \citep{davis1941}, using a bump chart to plot the rank order trajectory of persons across reflections. The rank order of people and groups in the $q^{th}$ centrality is plotted on the y-axis, and the centrality iteration $q$ is plotted on the x-axis. As the figure shows, $NORA$, $FLORA$, $CHARLOTTE$, and $EVELYN$ are the top-ranked actors when it comes to $C^R_p(2)$:  The average number of members of the groups they belong to. However, their fates in this reflective metric diverge at higher reflections, with $NORA$ and $FLORA$ maintaining their top positions but $CHARLOTTE$ and $EVELYN$ tumbling down the ranks, suggesting that the members of the groups they belong to affiliate with smaller groups than the members of the groups $NORA$ and $FLORA$ belong to (and so on for higher reflections). Notably, the reflective centrality rankings after freezing ($q \geq 18$) recover the Doreian et al. (2004) block partition (see Table~\ref{tab:southern}), but this time with Dorothy and Pearl in the middle separating the two largest blocks of women.

>>>>

\subsection{Empirical Example} \label{subsec:ex}
The following analyses use the classic Southern Women data \citep{davis1941} as the running example, a dataset that, according to \citet[p.]{freeman2003finding}, ``has become something of a touchstone for comparing analytic methods in social network analysis,'' having been analyzed ``again and again,'' and reappearing ``whenever any network analyst wants to explore the utility of some new tool for analyzing data.'' Freeman himself would go to review twenty-one such attempts, and the list has only gotten longer since his analytic ``meta-analysis'' \citep[e.g.,][]{doreian2004generalized, field2006identifying, roffilli2006identifying, wang2009exponential, everett2018measuring, lerner2022dynamic, batagelj2022analysis,  lizardo2024two}. As we can see, novel insights can still be garnered from these old data.

Figure~\ref{fig:p-refs} shows the trajectory of the HH reflective centralities for persons, using a bump chart to plot the rank order trajectory of persons across reflections. The rank order of people and groups in the $q^{th}$ centrality is plotted on the y-axis, and the centrality iteration $q$ is plotted on the x-axis. As the figure shows, $NORA$, $FLORA$, $CHARLOTTE$, and $EVELYN$ are the top-ranked actors when it comes to $C^R_p(2)$:  The average number of members of the groups they belong to. However, their fates in this reflective metric diverge at higher reflections, with $NORA$ and $FLORA$ maintaining their top positions but $CHARLOTTE$ and $EVELYN$ tumbling down the ranks, suggesting that the members of the groups they belong to affiliate with smaller groups than the members of the groups $NORA$ and $FLORA$ belong to (and so on for higher reflections). Notably, the reflective centrality rankings after freezing ($q \geq 18$) recover the Doreian et al. (2004) block partition (see Table~\ref{tab:southern}), but this time with Dorothy and Pearl in the middle separating the two largest blocks of women.
